Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-21 article.rnw
Move the part about intransitivity in the discussion to its own paragraph.
Use this to suggest future approaches: Bayesian or mixed membership.

We have shown that it is possible to fit a more parsimonious model of species interactions by grouping the interaction coefficients of species \emph{a posteriori}, and hence reducing the number of free parameters in the model.
Indeed, the results show that grouping species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}) than leaving them ungrouped.
Which grouping would give the most parsimonious model, however, could not be determined with confidence.
The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
% DBS: In my mind, I would steal the preceding sentence and spin it potentially spin it into its own paragraph later since it speaks strongly to a mixed-membership approach which could be sold as a "future direction".

@@

>>>>

We have shown that it is possible to fit a more parsimonious model of species interactions by grouping the interaction coefficients of species \emph{a posteriori}, and hence reducing the number of free parameters in the model.
Indeed, the results show that grouping species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}) than leaving them ungrouped.
Which grouping would give the most parsimonious model, however, could not be determined with confidence.

@@

The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
This could suggest a Bayesian approach, in which the outcome is not a definitive grouping, but a distribution of valid groupings.
Alternatively, it may suggest a mixed membership approach in which a species can be a partial part of more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.
